Considering scale in multilayer animal social networks

### 2020-06-26 paper/manuscript.Rmd
rm

### Temporal scale
#### Time windows 
We used a temporal multilayer network to assess the seasonality of caribou
sociality. Multilayer networks consisted of the social associations between 
`r DT[, uniqueN(get(idcol))]` individuals across 20 ordinal sample periods of 35-36 <!--QW: why 35-36 and not just 35 or 36?-->
days taken from the entire study period. Social associations were defined by
spatiotemporal overlap of individuals within 5 minutes and 50 m. For each time
window, we calculated individual graph strength within each
time window, and edge overlap and multidegree across time windows.

>>>>

### Temporal scale
#### Time windows 
We used a temporal multilayer network to assess the seasonality of caribou
sociality. Multilayer networks consisted of the social associations between 
`r DT[, uniqueN(get(idcol))]` individuals across 20 ordinal sample periods 
from the entire study period. Social associations were defined by
spatiotemporal overlap of individuals within 5 minutes and 50 m. For each time
window, we calculated individual graph strength within each
time window, and edge overlap and multidegree across time windows.
